A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-04 graph_syntax.tex
working...

The \emph{maximal connectivity graph} represents the first phase with all 
analysis codes being considered and all possible connections between them also present. The second graph 
is \emph{fundamental problem formulation graph}, which is the smallest possible graph 
that still fully defines a given problem formulation. Finally, a \emph{specific problem formulation} 
may be represented by including additional edges and node types to represent the 
solution strategy being employed to solve the problem.

@@

In addition to the four node types, there are three edge types:

\begin{description}
\item[fixed edge:] Fundamental, non-changeable property of a problem, such as 
  connections between related variable nodes. These 
edges can never be removed from a graph. 
\item[explicit edge:] Explicit exchange of information between two nodes. No node 
  can have more than a single incomming explicit edge. These edges are free and
  can be added or removed from the graph. 
\item [implicit edge:] Implicit passing of information from a driver node to a 
  variable node. A single variable node can have many incomming implicit edges. These edges are 
  free and can be added or removed from the graph. 
\end{description}

@@

@@

The driver node and the implicit edge are only allowed to be pressent in PSGs. All 
other node and edge types can be present in any of the three graphs, subject to a 
few restrictions: 
\begin{enumerate}
\item A model node can only have one edge directed to or from another model node.
\item A model node can only have fixed edges directed in or out.
\item A model node must have at least one edge directed in and at least one edge 
  directed out.
\item If a variable node has an outgoing edge to a model node then it may not have 
  any other outgoing edges.
\end{enumerate}

\subsection{In-degree and Out-degree}

The \emph{in-degree} of a node is the number of fixed or explicit edges directed in and 
is denoted as $\txt{deg}^-(v)$, and the \emph{out-degree} 
is the number of fixed or explicit edges directed out and it is denoted as $\txt{deg}^+(v)$.
We also define the \emph{upper in-degree limit}

\begin{equation}
\txt{deg}_u^-(v):V \to \mathbb{N}
\end{equation} 
and the \emph{lower in-degree limit}
\begin{equation}
\txt{deg}_l^-(v):V \to \mathbb{N}.
\end{equation}
These user-specified limits govern the number of explicit edges that may be directed into a 
node for a valid graph. Consider a variable node $v$ with
$\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, that node must have exactly one
incomming explicit edge or the graph is invalid. Two possiblities exist for voilating 
the limit conditions: 
\begin{description}
  \item[hole: ] The number of incomming edges is less than $\txt{deg}_l^-(v)$. 
    \begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \end{equation}
\end{description}

@@

Via the analysis block structure, we can also distinguish between input and ouptut
variable nodes. Inputs are any variable nodes that have an outgoing edge into a model 
node. Conversely, outputs are any variable nodes that have an incoming edge from a model node. 
Note that by this definition, inputs and outputs can only exist when variable nodes poses an 
edge joining them to a model node. In Fig. \ref{f:analysis block} these are labeled out as 
local inputs and local outputs. The variables are local because they are explicitely tied
to the analysis block and have no relevance without it.

MDAO problems require that information be passed between sets of analyses. When information from the output of one analysis 
block is passed, or connected, to the input of another analysis block, a new explicit edge is added 
connecting the two variable nodes involved in the exchange. Explicit edges are free because, unlike the edges 
within an analysis block, they could be added or removed depending on the demands of the specific problem. 
In other words, explicit edges are created by engineers linking the output of one tool to the input 
of another one. Note that it is allowed for a single output to have outgoing explicit edges to multiple 
other inputs. In Fig [insert ref], an output from analysis block A is connected 
to the inputs for both blocks B and C.

[[insert graph fig here]]

@@

More formally, any input variable that can be defined as a hole by Eqn. \ref{e:hole}
would be considered a design variable in the graph. When working with a MCG or FPG, only fixed and explicit edges are allowed, 
in which case a design variable is simply a variable node with no incomming edges. For a valid PSG 
any design variable node would have at least one (but possible multiple) incomming 
implicit edge from a driver node.

Objective and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
athrimetic opperations to form the final objective function. For example, the problem from 
Fig. \ref{f:designvars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer explictly identifies variables 
or groups of variables and assigns a simple, explicit relationship between them.

@@

\begin{comment}
The MDO problem formulation concepts represented by nodes are given in 
Table \ref{t:node representation}, and the concepts represented by edges are 
given in Table \ref{t:edge representation}.
% \begin{itemize}
% \item An objective or constraint is indicated by a variable node with no outgoing edges and with the incoming edges being directed from only other variable nodes.
% \item A global input is a variable node with no edges directed in and with at least two edges directed out to different variable nodes.
% \item A design variable is represented by a variable node with no edges directed in and on fixed edge directed out.
% \end{itemize}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by a node}
  \label{t:node representation}
  \begin{tabular}{ccc} \hline 
edges directed in & edges directed out & node representation \\ \hline
only explicit edges & none & objective or constraint\\
none & at least two explicit edges & global input \\
none & one fixed edge & design variable \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by an edge}
  \label{t:edge representation}
  \begin{tabular}{ccc} \hline 
from node & to node & edge representation \\ \hline
variable & variable & connection/passing of a variable\\
variable & model & local input \\
model & variable & local output \\
model & model & function call \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
%`Connection' edges connect the local outputs from one analysis block to input nodes.
\end{comment}

@@

A simple definition of a global node is any node that involves information 
from more than one analysis block. Likewise, a local node is any node 
that involves information from only a single analysis block. As stated before, variable 
nodes with fixed edges directed to model nodes (as part of an analysis block) are inherently local 
and similarly model nodes are also local. Expression and driver nodes
are not inherently local or global though. For these, their locality is determined 
by the incomming and outgoing edges they posses. Consider the graph in Fig [insert ref], 
where the expression node $g$ represents some kind of constraint for the optimziation problem. 
Since $g$ only had edges comming from analysis block $B$, it would be considered a local constraint 
on block $B$.

[[insert graph here]]

Although we've already established that variable nodes in an analysis block are local to that 
block, global design variables are a part of many MDAO problems. We've previously defined 
a design variable as any

While this simple definition is valid, it glosses over a more subtle aspect of 
some MDAO problems. Consider the graph in Fig. [insert ref], with three analysis 
blocks A, B, and C. The expression node, $g$, is a constraint that requires information 
from $A$ and $B$, so it would be considered global by the previous definition. Since $g$
has incomming edges from block $C$, it would not be global with respect to $C$. 
You could say that $g$ is local to the group $A,B$. In this sense, locality 
becomes a relative term. A given node can be local to a specific sub-graph of a large
problem. This subtle structure can become significant when determining how to partition 
an MDAO problem for use with certain MDAO architectures. Martins and Marriage 
demonstrate how Collaborative Optimization outperforms MultiDisciplinary Feasible
when they separated a problem into two sub-problems with variables, objectives, and 
constraints local to each one\cite{Marriage2008a}.

@@

\subsection{Multi-fidelity Analyses}

\section{Building MCG, FPG, and PSG}

\subsection{Maximal Connectivity Graph}
To construct the maximal connectivity graph, we assume that a set of codes, global inputs, and objectives and constraints (collectively called global outputs) are provided. The codes are represented by analysis block graphs ((ABGs?)) $A_i=(V_{A_i},E_{A_i}), \ i\in I$, where $m$ is the number of codes and $I=\{1,2,\ldots,m\}$. The global inputs are represented as a set of variable nodes $V_\txt{in}$, and the global outputs are represented by a set of variable nodes $V_\txt{out}$. 
We assume that $V_\txt{in}$, $V_\txt{out}$, and each $A_i$ are given, and that any potential connection between variables is given in the form of explicit edges in the set $C_M$. 
Then we may construct the maximal connectivity graph $M=(V_M,E_M)$ as
\begin{IEEEeqnarray*}{rCl}
V_M & = & V_\txt{in} \cup V_\txt{out} \cup \left( \bigcup_{i \in I} V_{A_i} \right), \\
E_M & = & C_M \cup \left( \bigcup_{i \in I} E_{A_i} \right),
\end{IEEEeqnarray*}
The MCG $M$ is uniquely determined by the given set of analysis blocks, the required outputs, and the given global inputs. In the cases where the set of global inputs is not known a priori, the process of obtaining the FPG will reveal the required inputs, as discussed subsequently.

@@

The set $C_F$ is a set containing explicit edges representing connections. Since $C_M$ is the set of all potential connections, we must have $C_F \subset C_M$. While no other conditions are explicitly stated for $C_F$, requirement (6) is actually a requirement on both $I_F$ and $C_F$.

\subsection{Obtaining the Fundamental Problem Graph}
In general, there may be multiple different graphs that satisfy the FPG conditions, though there may be none at all. Here, we describe a process for obtaining an FPG by starting with the MCG and disconnecting explicit edges until the FPG conditions are met. Then the problem is reduced to deciding which explicit edges to remove.

%Then, mathematically, the FPG starts with $\mathcal A_1 = \{1,\ldots,m\}$, $I_{F,1} = I$, and $C_{F,1} = C_M$.
Then, mathematically, the FPG starts with $C_{F,0} = C_M$, $E_{F,0} = E_M$, $V_{F,0} = V_M$.
The nodes where $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ are considered first.
\begin{enumerate}
\item The first step is to detect holes and disconnect the explicit edges following them. These explicit edges are removed because they represent variables which cannot be determined because the analysis function does not have adequate inputs. The set of variable nodes which are holes is created as
\begin{equation}
H = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) < \txt{deg}_l^-(v) \},
\end{equation}
which is the set of variable nodes with fewer incoming edges than are allowed by the lower in-degree limit.
Then the updated set of edges is created by removing the first set of explicit edges following the hole:
\begin{equation}
C_{F,1} = C_{F,0} \setminus \{(x,y) \in E_M \st x=E_M^3(v) \txt{ for } v \in H\},
\end{equation}
%deg-v is now recaculated for the new C. 
and this step is demonstrated by Fig.~\ref{f:hole}. Because removing these edges can create new holes, this step must be repeated until no more holes are found.
\begin{figure}[htb!]
	\begin{center}
	\includegraphics[width=3in]{images/analysis_block_hole}
	\end{center}
	\vspace{-20pt}
\caption{Example variable node indicating a hole.}
\label{f:hole}
\end{figure}

\item The second step is to detect collisions and to then disconnect enough explicit edges so that the collisions are resolved. The set of variable nodes which contain collisions is created as
\begin{equation}
S_\txt{nodes} = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) > \txt{deg}_u^-(v) \}.
\end{equation}
For each collision node we can construct a set contained the edges directed in. The set containing all of these sets is constructed as
\begin{equation}
S_\txt{edges} = \big \{ \{(x,y) \in E_M\} \st y \in S_\txt{nodes} \big \}
\end{equation}
Let $J=\{1,2,\ldots,|S_\txt{edges}|\}$ be an indexing set for $S_\txt{edges}$ such that each $S_{\txt{edges},j}$ corresponds to a set in $S_\txt{edges}$ for $j \in J$. 
An example collision is shown in Fig.~\ref{f:collision} to indicate the definition of $S_{\txt{edges},j}$. 
We can assume that $J$ also indexes $S_\txt{nodes}$ because there is a one--to--one correspondence between the elements in $S_\txt{nodes}$ and the elements in $S_\txt{edges}$ (which are sets). 
Then we may construct sets of edges as
\begin{equation}
B_j = \big \{e_k \in S_{\txt{edges},j} \st k \in \{1,2,\ldots,K\} \txt{ with } K \leq \txt{deg}_u^-(v_j) \big \}, \ j \in J,
\end{equation}
which means that each set $B_j$ is constructed from the set $S_{\txt{edges},j}$ by taking only as many edges as are allowed by the upper in--degree limit of $v_j$. The construction of each $B_j$ corresponds to making a decision on which edges to include and which edges not to include. Then let
\begin{equation}
C_{F,2} = \{ e \in C_{F,1} \st e \in B_j \txt{ for some } j \in J\},
\end{equation}
\begin{equation}
E_{F,2} = E_M \setminus (C_M \setminus C_{F,2})
\end{equation}
and
\begin{equation}
F_2 = (V_M,E_{F,2})
\end{equation}
\begin{figure}[htb!]
	\begin{center}
	\includegraphics[width=3in]{images/analysis_block_collision}
	\end{center}
	\vspace{-20pt}
\caption{Example variable node indicating a collision.}
\label{f:collision}
\end{figure}

@@

    \subsection{Solution Graph Syntax}
    What is the difference between a problem formulation and a problem solution method? Convert from a cyclic graph, to an acyclic graph
    \begin{itemize}
        \item Cycles indicate convergence loops or design variable loops
        \item Problem can't be solved until all loops are *removed* by adding solvers/optimizers
        \item *Special* nodes for solvers and optimizers that *break* loops (from an algorithmic point of view)
        \item FPG represents the minimal amount of information necessary to define a problem
        \item Any solution path grows the graph complexity by adding edges and nodes (or possibly have an empty solution graph, which you build up
        as you remove edges from problem formulation graph?)
    \end{itemize}

>>>>

The \emph{maximal connectivity graph} represents the first phase with all 
analysis codes being considered and all possible connections between them also present. The second graph 
is \emph{fundamental problem formulation graph}, which is the smallest possible graph 
that still fully defines a given problem formulation. Finally, a \emph{specific problem formulation} 
may be represented by including additional edges and nodes to represent the 
solution strategy being employed to solve the problem.

@@

In addition to the four node types, there are two edge types:

\begin{description}
\item[connection edge:] Exchange of information between two nodes. These edges 
can either be fixed (can not be removed from graph) or free (can be removed). 
\item [implicit edge:] Implicit passing of information from a driver node to a 
  variable node. A single variable node can have many incomming implicit edges. These edges are 
  free and can be added or removed from the graph. 
\end{description}

@@

In Alexandrov and Lewis's REMS syntax only two node types were present, variable 
and function, and only one edge type\cite{alexandrov2004}. We've chosen to rename the ``function'' node 
type to ``model'' to be more consistent with modern MDAO frameworks. This work 
adds two more node types and one more edge type to the syntax to allow descriptive
graphs for all three phases of the design process.

@@

The driver node and the implicit edge are only allowed to be pressent in PSGs. All 
other node and edge types can be present in any of the three graphs, subject to a 
few restrictions: 
\begin{enumerate}
\item A model node can only have one edge directed to or from another model node.
\item A model node can only have fixed connection edges directed in or out.
\item A model node must have at least one edge directed in and at least one edge 
  directed out.
\item If a variable node has an outgoing edge to a model node then it may not have 
  any other outgoing edges.
\end{enumerate}

\subsection{In-degree and Out-degree}
\label{s:indegree-outdegree}
The \emph{in-degree} of a node is the number of connection edges directed in and 
is denoted as $\txt{deg}^-(v)$, and the \emph{out-degree} 
is the number of connection edges directed out and it is denoted as $\txt{deg}^+(v)$.
The degree of a given node is only a function of the connection edges 
attached to it. The number of implicit edges is not relevant since any number 
of drivers could be involved, at different parts of an solution process. For 
example in a sequential optimization where a global optimizer is first applied
and a gradient based one is applied second, design variables would have incomming 
implicit edges from both optimizers but this would not affect the in-degree of those
variable nodes.

We also define the \emph{upper in-degree limit}

\begin{equation}
\txt{deg}_u^-(v):V \to \mathbb{N}
\end{equation} 
and the \emph{lower in-degree limit}
\begin{equation}
\txt{deg}_l^-(v):V \to \mathbb{N}.
\end{equation}
These user-specified limits govern the number of fixed and connection edges that 
may be directed into a node for a valid graph. Consider a variable node $v$ with
$\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, that node must have exactly one
incomming edge or the graph is invalid. Two possiblities exist for voilating 
the limit conditions: 
\begin{description}
  \item[hole: ] The number of incomming edges is less than $\txt{deg}_l^-(v)$. 
    \begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \label{e:collision} \end{equation}
\end{description}

@@

Via the analysis block structure, we can also distinguish between input and ouptut
variable nodes. Inputs are any variable nodes that have an outgoing edge into a model 
node. Conversely, outputs are any variable nodes that have an incoming edge from a model node. 
Note that by this definition, inputs and outputs can only exist when variable nodes poses an 
edge joining them to a model node. In Fig. \ref{f:analysis block} these are labeled out as 
local inputs and local outputs. The variables are local because they are explicitly tied
to the analysis block and have no relevance without it.

MDAO problems require that information be passed between sets of analyses. When 
information from the output of one analysis block is passed, or connected, to the 
input of another analysis block, a new connection edge is added connecting the two 
variable nodes involved in the exchange. These connection edges are free, unlike the edges 
within an analysis block, they could be added or removed depending on the needs
of a given design problem. In other words, free connection edges are created by 
engineers linking the output of one tool to the input of another one. Note that 
it is allowed for a single output to have outgoing connection edges to multiple 
downstream inputs.

@@

More formally, any input variable that can be defined as a hole by Eqn. \ref{e:hole}
would be considered a design variable in the graph. When working with a MCG or 
FPG, only connection edges are allowed, in which case a design variable 
is simply a variable node with no incomming edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

Objective and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
athrimetic opperations to form the final objective function. For example, the problem from 
Fig. \ref{f:designvars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer identifies variables 
or groups of variables and assigns a simple relationship between them.

@@

@@

  A simple definition of a global node is any node that involves information 
  from more than one analysis block. Likewise, a local node is any node 
  that involves information from only a single analysis block. As stated before, variable 
  nodes with fixed edges directed to model nodes (as part of an analysis block) are inherently local 
  and similarly model nodes are also local. Expression and driver nodes
  are not inherently local or global though. For these, their locality is determined 
  by the incomming and outgoing edges they possess. Consider the graph in Fig. \ref{f:local_global}, 
  where the expression node $g_1$ represents some kind of constraint for the optimziation problem. 
  Since $g_1$ only has edges comming from analysis block $B$, it would be considered a local constraint 
  on block $B$. $g_2$ has incomming edges from both $A$ and $B$ analysis blocks, so it would be a global constraint.

  \begin{figure}
      \begin{center}
      %\includegraphics[height=.25\textheight]{XDSM/simple}
      [[insert graph here]]
      \caption{A simple graph with local and global nodes \label{f:local_global}}
      \end{center}
  \end{figure}

  Although we've already established that variable nodes in an analysis block are local to that 
  block, global variables are a part of many MDAO problems and must be representable. A global variable 
  would be any variable node with multiple outgoing connection edges. 
  For example, in Fig. \ref{f:local_global} the global node $w^*$ has outgoing edges to 
  the $w$ variable nodes feeding both $A$ and $B$ analysis blocks.

  While this simple definition is valid, it glosses over a more subtle aspect of 
  some MDAO problems. Fig. \ref{f:local_global}, has three analysis 
  blocks A, B, and C. Above we identified node $g_2$ as global,  but
  it has no incomming edges from block $C$. So you could say that $g_2$ is 
  local to the the set of blocks $A,B$. In this sense, locality 
  becomes a relative term. A given node can be local to a specific sub-graph of a large
  problem. This subtle structure can become significant when determining how to 
  effectively partition an MDAO problem into sub-problems 
  \cite{krishnamachari1997optimal,allison2009optimal,michelena1997hypergraph}.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. Consider the notional problem from section \ref{sec:spg_vs_fpg} where two 
  analyses, $A$ and $B$ are coupled through their respective variables. The graph of this 
  is shown in Fig. \ref{f:coupling}. In the graph $A.z$ has an outgoing connection 
  edge to $B.z$, indicating that there is a connection between the two. 
  Similarly a connection exists between $B.y$ and $A.y$. These two connections form 
  a cycle which represent the coupling between them. This cycle means that blocks $A$ and $B$ need
  to be iterated on untill they converge.

  \begin{figure}
      \begin{center}
      %\includegraphics[height=.25\textheight]{}
      [INSERT GRAPH HERE]
      \caption{Graph of a notional problem with simple coupling \label{f:coupling}}
      \end{center}
  \end{figure}

  It is important to note that the cycle in graph in Fig. \ref{f:coupling} does not contain 
  any driver nodes. That means that no solver, optimizer, or other iterative construct is 
  invovled in the coupling. This absence is intentional, as the coupling is an inherant part 
  of the problem. This corresponds directly To Eqn. \ref{eqn:simple_fpf}, where 
  each equality constraint is one edge in the graph. Transitionining to either 
  Eqn. \ref{eqn:simple} or Eqn. \ref{eqn:simple2} means selecting one of the nodes as the starting point 
  for the iteration, indicating the associated analysis block should be executed first.

  Larger problems can contain more complex cycles in thier FPG, indicating more 
  complex coupling between analyses. A cycle can contain more than 
  just two analysis blocks. Multiple independent cycles can exist, indicating 
  independent coupling relationships. Cycles can also overlap, where the same analysis 
  blocks are involved in multiple different coupling cycles. All of these situations
  arise naturally as the size of problems grows, and managing all of this coupling 
  becomes difficult. From the perspective of the graph, the problem reduces down to 
  a ordering challenge. For each cycle in the graph, you need to pick a analysis block
  to start the iteration from. Rogers DEMAID tool uses a genetic algorithm to find an ordering 
  that minimizes the overall coupling of the system by separating independent 
  cycles in the graph \cite{rogers1996,rogers1996demaid}.

\subsection{Multi-fidelity Problems}

  A multi-fidelity problem can be characterized by two or more different analyses 
  each calculating the same data. Mapping this type of multi-fidelity situation 
  onto a graph will yeild two analysis blocks, each with thier own output 
  variable nodes, having outgoing edges to a third analysis block that needs the 
  data as input. Figure \ref{f:collision-example} shows a notional problem 
  that exhibits this structure, where the key feature is that variable node $y$ in 
  analysis block $C$ has two incomming edges.

  \begin{figure}
      \begin{center}
      %\includegraphics[height=.25\textheight]{}
      [INSERT GRAPH HERE]
      \caption{Graph of a notional multi-fidelity problem \label{f:collision-example}}
      \end{center}
  \end{figure}

  When an input variable node has more than one incomming edge, designers must make
  some kind of decision about how to manage the flow of information in their problem. 
  In Eqn. \ref{e:collision} we defined a collision as the situation where
  there are more incomming connection edges than the ${deg}_u^-(y)$. So desginers can
  indicate how to handle conflicting edges in a problem graph by setting the ${deg}_u^-(y)$
  for a given node. In more concrete terms, setting this limit equates to defining 
  the part of the graph in question as single or multi-fidelity.

  When ${deg}_u^-(y)=1$, then any conflicting edges in the graph will cause a collision
  and a choice between the colliding analysis blocks must be made. This results in a 
  single fidelity design problem. On the other hand if ${deg}_u^-(y)=2$, then two 
  different analysis blocks can co-exist with a given graph without causing a 
  collision. The design problem is then a multi-fidelity problem.

  Multi-fidelity problems are always charaterized by graphs with variable 
  nodes that have an upper-degree-limit greater than one. These problems require 
  special techniques for resolving the confliciting edges by introducing some mechanism
  to manage when each of the different fidelity analyses are 
  run\cite{march2012provably,alexandrov2001approximation,Huang_Allen_Notz_Miller_2006}.

\section{Building MCG and FPG}

\subsection{Maximal Connectivity Graph}
  To construct the maximal connectivity graph, we assume that a set of codes, global inputs, and objectives and constraints (collectively called global outputs) are provided. The codes are represented by analysis block graphs ((ABGs?)) $A_i=(V_{A_i},E_{A_i}), \ i\in I$, where $m$ is the number of codes and $I=\{1,2,\ldots,m\}$. The global inputs are represented as a set of variable nodes $V_\txt{in}$, and the global outputs are represented by a set of variable nodes $V_\txt{out}$. 
  We assume that $V_\txt{in}$, $V_\txt{out}$, and each $A_i$ are given, and that any potential connection between variables is given in the form of connection edges in the set $C_M$. 
  Then we may construct the maximal connectivity graph $M=(V_M,E_M)$ as
  \begin{IEEEeqnarray*}{rCl}
  V_M & = & V_\txt{in} \cup V_\txt{out} \cup \left( \bigcup_{i \in I} V_{A_i} \right), \\
  E_M & = & C_M \cup \left( \bigcup_{i \in I} E_{A_i} \right),
  \end{IEEEeqnarray*}
  The MCG $M$ is uniquely determined by the given set of analysis blocks, the required outputs, and the given global inputs. In the cases where the set of global inputs is not known a priori, the process of obtaining the FPG will reveal the required inputs, as discussed subsequently.

@@

The set $C_F$ is a set containing connection edges representing connections. Since $C_M$ is the set of all potential connections, we must have $C_F \subset C_M$. While no other conditions are explicitly stated for $C_F$, requirement (6) is actually a requirement on both $I_F$ and $C_F$.

\subsection{Obtaining the Fundamental Problem Graph}
In general, there may be multiple different graphs that satisfy the FPG conditions, though there may be none at all. Here, we describe a process for obtaining an FPG by starting with the MCG and disconnecting connection edges until the FPG conditions are met. Then the problem is reduced to deciding which connection edges to remove.

%Then, mathematically, the FPG starts with $\mathcal A_1 = \{1,\ldots,m\}$, $I_{F,1} = I$, and $C_{F,1} = C_M$.
Then, mathematically, the FPG starts with $C_{F,0} = C_M$, $E_{F,0} = E_M$, $V_{F,0} = V_M$.
The nodes where $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ are considered first.
\begin{enumerate}
\item The first step is to detect holes and disconnect the connection edges following them. These connection edges are removed because they represent variables which cannot be determined because the analysis function does not have adequate inputs. The set of variable nodes which are holes is created as
\begin{equation}
H = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) < \txt{deg}_l^-(v) \},
\end{equation}
which is the set of variable nodes with fewer incoming edges than are allowed by the lower in-degree limit.
Then the updated set of edges is created by removing the first set of connection edges following the hole:
\begin{equation}
C_{F,1} = C_{F,0} \setminus \{(x,y) \in E_M \st x=E_M^3(v) \txt{ for } v \in H\},
\end{equation}
%deg-v is now recaculated for the new C. 
and this step is demonstrated by Fig.~\ref{f:hole}. Because removing these edges can create new holes, this step must be repeated until no more holes are found.
\begin{figure}[htb!]
	\begin{center}
	\includegraphics[width=3in]{images/analysis_block_hole}
	\end{center}
	\vspace{-20pt}
\caption{Example variable node indicating a hole.}
\label{f:hole}
\end{figure}

\item The second step is to detect collisions and to then disconnect enough connection edges so that the collisions are resolved. The set of variable nodes which contain collisions is created as
\begin{equation}
S_\txt{nodes} = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) > \txt{deg}_u^-(v) \}.
\end{equation}
For each collision node we can construct a set contained the edges directed in. The set containing all of these sets is constructed as
\begin{equation}
S_\txt{edges} = \big \{ \{(x,y) \in E_M\} \st y \in S_\txt{nodes} \big \}
\end{equation}
Let $J=\{1,2,\ldots,|S_\txt{edges}|\}$ be an indexing set for $S_\txt{edges}$ such that each $S_{\txt{edges},j}$ corresponds to a set in $S_\txt{edges}$ for $j \in J$. 
An example collision is shown in Fig.~\ref{f:collision} to indicate the definition of $S_{\txt{edges},j}$. 
We can assume that $J$ also indexes $S_\txt{nodes}$ because there is a one--to--one correspondence between the elements in $S_\txt{nodes}$ and the elements in $S_\txt{edges}$ (which are sets). 
Then we may construct sets of edges as
\begin{equation}
B_j = \big \{e_k \in S_{\txt{edges},j} \st k \in \{1,2,\ldots,K\} \txt{ with } K \leq \txt{deg}_u^-(v_j) \big \}, \ j \in J,
\end{equation}
which means that each set $B_j$ is constructed from the set $S_{\txt{edges},j}$ by taking only as many edges as are allowed by the upper in--degree limit of $v_j$. The construction of each $B_j$ corresponds to making a decision on which edges to include and which edges not to include. Then let
\begin{equation}
C_{F,2} = \{ e \in C_{F,1} \st e \in B_j \txt{ for some } j \in J\},
\end{equation}
\begin{equation}
E_{F,2} = E_M \setminus (C_M \setminus C_{F,2})
\end{equation}
and
\begin{equation}
F_2 = (V_M,E_{F,2})
\end{equation}
\begin{figure}[htb!]
	\begin{center}
	\includegraphics[width=3in]{images/analysis_block_collision}
	\end{center}
	\vspace{-20pt}
\caption{Example variable node indicating a collision.}
\label{f:collision}
\end{figure}

@@
